---
author: Guillaume Chomicki1*, Gustavo G. Burin2, Toby ??, Susanne S. Renner3
title: The effects of mutualism on trait evolution - Residuals from ClimPC
output:
  pdf_document:
    toc: true
    extra_dependencies: ["float"]
    latex_engine: xelatex
  html_document:
    toc: true
    toc_float: true
header-includes:
  - \usepackage{pdflscape}
---

Submitted to Ecology Letters, Evolution or Evolution Letters – well let’s see what we find!

Affiliations: 1Department of Bioscience, Durham University, Stockton Rd., Durham DH1 3LE, UK. 2University of Sao Paulo, xxxxx. 3Systematic Botany and Mycology, Department of Biology, University of Munich (LMU), Menzinger Str. 67, 80638 Munich, Germany.

Correspondence: *guillaume.chomicki@durham.ac.uk

# Analyses accounting for climate

The results below follow the same rationale as the ones from the main document. However, in the cases below all analyses use the plant traits already accounted for climatic effects by using the residuals from the regressions between each trait and the first three Principal Components of the climatic variables obtained from BioClim (REF).

\newpage

# Methods

```{r setup, eval = FALSE, echo = FALSE}

here::i_am("manuscript/chomicki_et_al_climpc_clean.Rmd")

source(here::here("R/tree_plots.R"))
library("knitr")
library("RColorBrewer")
# load("../output/first_analysis.RData")
knitr::opts_chunk$set(fig.pos = "h", out.extra = "")
# source("../R/ouwie_summary_mcc.R")
pars.table.pc1 <- read.csv(here::here("output/fullpar_table_climpc1.csv"))
pars.table.pc1$trait <- c("Stem Area", "Leaf Area", "Corola Length", "Petiole Length", "Hole Diameter")[match(pars.table.pc1$trait, c("stemarea", "leafarea", "corleng", "petleng", "holediam"))]
pars.table.pc2 <- read.csv(here::here("output/fullpar_table_climpc2.csv"))
pars.table.pc2$trait <- c("Stem Area", "Leaf Area", "Corola Length", "Petiole Length", "Hole Diameter")[match(pars.table.pc2$trait, c("stemarea", "leafarea", "corleng", "petleng", "holediam"))]
pars.table.pc3 <- read.csv(here::here("output/fullpar_table_climpc3.csv"))
pars.table.pc3$trait <- c("Stem Area", "Leaf Area", "Corola Length", "Petiole Length", "Hole Diameter")[match(pars.table.pc3$trait, c("stemarea", "leafarea", "corleng", "petleng", "holediam"))]
colors <- setNames(brewer.pal(4, "Set1"), 1:4)

```

```{r pars_ouwie_setup, echo = FALSE, message = FALSE, warning = FALSE}

library("cowplot")
library("patchwork")

data.plot.pc1 <- reshape2::melt(pars.table.pc1[pars.table.pc1$trait == "Hole Diameter",], id.vars = c("trait", "disc.trait", "simmap"))
theta.plot.pc1 <- data.plot.pc1[grep("theta", data.plot.pc1$variable),]
alpha.plot.pc1 <- data.plot.pc1[grep("alpha", data.plot.pc1$variable),]
sigma.plot.pc1 <- data.plot.pc1[grep("sigma", data.plot.pc1$variable),]

data.plot.pc2 <- reshape2::melt(pars.table.pc2[pars.table.pc2$trait == "Hole Diameter",], id.vars = c("trait", "disc.trait", "simmap"))
theta.plot.pc2 <- data.plot.pc2[grep("theta", data.plot.pc2$variable),]
alpha.plot.pc2 <- data.plot.pc2[grep("alpha", data.plot.pc2$variable),]
sigma.plot.pc2 <- data.plot.pc2[grep("sigma", data.plot.pc2$variable),]

data.plot.pc3 <- reshape2::melt(pars.table.pc3[pars.table.pc3$trait == "Hole Diameter",], id.vars = c("trait", "disc.trait", "simmap"))
theta.plot.pc3 <- data.plot.pc3[grep("theta", data.plot.pc3$variable),]
alpha.plot.pc3 <- data.plot.pc3[grep("alpha", data.plot.pc3$variable),]
sigma.plot.pc3 <- data.plot.pc3[grep("sigma", data.plot.pc3$variable),]

source(here::here("R/data_prep_ouwie_climpc_clean.R"))

```

# Appendages

# PC1 - Parameters

```{r results = 'asis', echo = FALSE}

if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}

```

```{r pars_ouwie_app_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Appendage."}

theta.app.plot.pc1 <- subset(theta.plot.pc1, disc.trait == "app")
theta.app.plot.pc1$variable <- as.character(theta.app.plot.pc1$variable)
theta.app.plot.pc1 <- theta.app.plot.pc1[theta.app.plot.pc1$value >= -10 & theta.app.plot.pc1$value <= 10, ]

alpha.app.plot.pc1 <- subset(alpha.plot.pc1, disc.trait == "app")
alpha.app.plot.pc1$variable <- as.character(alpha.app.plot.pc1$variable)
alpha.app.plot.pc1 <- alpha.app.plot.pc1[alpha.app.plot.pc1$value >= -10 & alpha.app.plot.pc1$value <= 10, ]

sigma.app.plot.pc1 <- subset(sigma.plot.pc1, disc.trait == "app")
sigma.app.plot.pc1$variable <- as.character(sigma.app.plot.pc1$variable)
sigma.app.plot.pc1 <- sigma.app.plot.pc1[sigma.app.plot.pc1$value >= -10 & sigma.app.plot.pc1$value <= 10, ]

theta.app.pc1 <-
    ggplot(na.omit(theta.app.plot.pc1)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.app) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

alpha.app.pc1 <-
    ggplot(na.omit(alpha.app.plot.pc1)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.app) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

sigma.app.pc1 <-
    ggplot(na.omit(sigma.app.plot.pc1)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.app) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Sigma") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          #strip.background.y = element_blank(),
          #strip.text.y = element_blank(),
          axis.title.x = element_blank())

(theta.app.pc1 + alpha.app.pc1 + sigma.app.pc1) +
    plot_annotation(tag_levels = 'A')

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

## PC1 - Parameter differences

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r diffs_theta_ouwie_app_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Appendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("app.diff.theta.pc1.", gsub(" ", ".", agg.app.diff.pc1$Group.1)), get)), format = "latex", caption = "Differences in Theta values for PC1 analysis of Appendages. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.app, length(agg.app.diff.pc1$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.app.diff.pc1$Group.1), c(1, rep(length(states.app), length(agg.app.diff.pc1$Group.1)))))

```

```{r diffs_alpha_ouwie_app_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Appendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("app.diff.alpha.pc1.", gsub(" ", ".", agg.app.diff.pc1$Group.1)), get)), format = "latex", caption = "Differences in Alpha values for PC1 analysis of Appendages. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.app, length(agg.app.diff.pc1$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.app.diff.pc1$Group.1), c(1, rep(length(states.app), length(agg.app.diff.pc1$Group.1)))))

```

```{r diffs_sigma_ouwie_app_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Appendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("app.diff.sigma.pc1.", gsub(" ", ".", agg.app.diff.pc1$Group.1)), get)), format = "latex", caption = "Differences in Sigma values for PC1 analysis of Appendages. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.app, length(agg.app.diff.pc1$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.app.diff.pc1$Group.1), c(1, rep(length(states.app), length(agg.app.diff.pc1$Group.1)))))

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

# PC2 - Parameters

```{r results = 'asis', echo = FALSE}

if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}

```

```{r pars_ouwie_app_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Appendage."}

theta.app.plot.pc2 <- subset(theta.plot.pc2, disc.trait == "app")
theta.app.plot.pc2$variable <- as.character(theta.app.plot.pc2$variable)
theta.app.plot.pc2 <- theta.app.plot.pc2[theta.app.plot.pc2$value >= -10 & theta.app.plot.pc2$value <= 10, ]

alpha.app.plot.pc2 <- subset(alpha.plot.pc2, disc.trait == "app")
alpha.app.plot.pc2$variable <- as.character(alpha.app.plot.pc2$variable)
alpha.app.plot.pc2 <- alpha.app.plot.pc2[alpha.app.plot.pc2$value >= -10 & alpha.app.plot.pc2$value <= 10, ]

sigma.app.plot.pc2 <- subset(sigma.plot.pc2, disc.trait == "app")
sigma.app.plot.pc2$variable <- as.character(sigma.app.plot.pc2$variable)
sigma.app.plot.pc2 <- sigma.app.plot.pc2[sigma.app.plot.pc2$value >= -10 & sigma.app.plot.pc2$value <= 10, ]

theta.app.pc2 <-
    ggplot(na.omit(theta.app.plot.pc2)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.app) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

alpha.app.pc2 <-
    ggplot(na.omit(alpha.app.plot.pc2)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.app) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

sigma.app.pc2 <-
    ggplot(na.omit(sigma.app.plot.pc2)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.app) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Sigma") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          #strip.background.y = element_blank(),
          #strip.text.y = element_blank(),
          axis.title.x = element_blank())

(theta.app.pc2 + alpha.app.pc2 + sigma.app.pc2) +
    plot_annotation(tag_levels = 'A')

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

## PC2 - Parameter differences

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r diffs_theta_ouwie_app_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Appendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("app.diff.theta.pc2.", gsub(" ", ".", agg.app.diff.pc2$Group.1)), get)), format = "latex", caption = "Differences in Theta values for PC2 analysis of Appendages. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.app, length(agg.app.diff.pc2$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.app.diff.pc1$Group.1), c(1, rep(length(states.app), length(agg.app.diff.pc1$Group.1)))))

```

```{r diffs_alpha_ouwie_app_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Appendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("app.diff.alpha.pc2.", gsub(" ", ".", agg.app.diff.pc2$Group.1)), get)), format = "latex", caption = "Differences in Alpha values for PC2 analysis of Appendages. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.app, length(agg.app.diff.pc2$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.app.diff.pc1$Group.1), c(1, rep(length(states.app), length(agg.app.diff.pc1$Group.1)))))

```

```{r diffs_sigma_ouwie_app_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Appendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("app.diff.sigma.pc2.", gsub(" ", ".", agg.app.diff.pc2$Group.1)), get)), format = "latex", caption = "Differences in Sigma values for PC2 analysis of Appendages. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.app, length(agg.app.diff.pc2$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.app.diff.pc1$Group.1), c(1, rep(length(states.app), length(agg.app.diff.pc1$Group.1)))))

```


```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

# PC3 - Parameters

```{r results = 'asis', echo = FALSE}

if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}

```

```{r pars_ouwie_app_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Appendage."}

theta.app.plot.pc3 <- subset(theta.plot.pc3, disc.trait == "app")
theta.app.plot.pc3$variable <- as.character(theta.app.plot.pc3$variable)
theta.app.plot.pc3 <- theta.app.plot.pc3[theta.app.plot.pc3$value >= -10 & theta.app.plot.pc3$value <= 10, ]

alpha.app.plot.pc3 <- subset(alpha.plot.pc3, disc.trait == "app")
alpha.app.plot.pc3$variable <- as.character(alpha.app.plot.pc3$variable)
alpha.app.plot.pc3 <- alpha.app.plot.pc3[alpha.app.plot.pc3$value >= -10 & alpha.app.plot.pc3$value <= 10, ]

sigma.app.plot.pc3 <- subset(sigma.plot.pc3, disc.trait == "app")
sigma.app.plot.pc3$variable <- as.character(sigma.app.plot.pc3$variable)
sigma.app.plot.pc3 <- sigma.app.plot.pc3[sigma.app.plot.pc3$value >= -10 & sigma.app.plot.pc3$value <= 10, ]

theta.app.pc3 <-
    ggplot(na.omit(theta.app.plot.pc3)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.app) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

alpha.app.pc3 <-
    ggplot(na.omit(alpha.app.plot.pc3)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.app) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

sigma.app.pc3 <-
    ggplot(na.omit(sigma.app.plot.pc3)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.app) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Sigma") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          #strip.background.y = element_blank(),
          #strip.text.y = element_blank(),
          axis.title.x = element_blank())

(theta.app.pc3 + alpha.app.pc3 + sigma.app.pc3) +
    plot_annotation(tag_levels = 'A')

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

## PC3 - Parameter differences

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r diffs_theta_ouwie_app_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Appendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("app.diff.theta.pc3.", gsub(" ", ".", agg.app.diff.pc3$Group.1)), get)), format = "latex", caption = "Differences in Theta values for PC3 analysis of Appendages. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.app, length(agg.app.diff.pc3$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.app.diff.pc1$Group.1), c(1, rep(length(states.app), length(agg.app.diff.pc1$Group.1)))))
```

```{r diffs_alpha_ouwie_app_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Appendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("app.diff.alpha.pc3.", gsub(" ", ".", agg.app.diff.pc3$Group.1)), get)), format = "latex", caption = "Differences in Alpha values for PC3 analysis of Appendages. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.app, length(agg.app.diff.pc3$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.app.diff.pc1$Group.1), c(1, rep(length(states.app), length(agg.app.diff.pc1$Group.1)))))

```

```{r diffs_sigma_ouwie_app_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Appendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("app.diff.sigma.pc3.", gsub(" ", ".", agg.app.diff.pc3$Group.1)), get)), format = "latex", caption = "Differences in Sigma values for PC3 analysis of Appendages. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.app, length(agg.app.diff.pc3$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.app.diff.pc1$Group.1), c(1, rep(length(states.app), length(agg.app.diff.pc1$Group.1)))))

```


```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```






# Architecture

# PC1 - Parameters

```{r results = 'asis', echo = FALSE}

if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}

```

```{r pars_ouwie_arch_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Archendage."}

theta.arch.plot.pc1 <- subset(theta.plot.pc1, disc.trait == "arch")
theta.arch.plot.pc1$variable <- as.character(theta.arch.plot.pc1$variable)
theta.arch.plot.pc1 <- theta.arch.plot.pc1[theta.arch.plot.pc1$value >= -10 & theta.arch.plot.pc1$value <= 10, ]

alpha.arch.plot.pc1 <- subset(alpha.plot.pc1, disc.trait == "arch")
alpha.arch.plot.pc1$variable <- as.character(alpha.arch.plot.pc1$variable)
alpha.arch.plot.pc1 <- alpha.arch.plot.pc1[alpha.arch.plot.pc1$value >= -10 & alpha.arch.plot.pc1$value <= 10, ]

sigma.arch.plot.pc1 <- subset(sigma.plot.pc1, disc.trait == "arch")
sigma.arch.plot.pc1$variable <- as.character(sigma.arch.plot.pc1$variable)
sigma.arch.plot.pc1 <- sigma.arch.plot.pc1[sigma.arch.plot.pc1$value >= -10 & sigma.arch.plot.pc1$value <= 10, ]

theta.arch.pc1 <-
    ggplot(na.omit(theta.arch.plot.pc1)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.arch) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

alpha.arch.pc1 <-
    ggplot(na.omit(alpha.arch.plot.pc1)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.arch) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

sigma.arch.pc1 <-
    ggplot(na.omit(sigma.arch.plot.pc1)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.arch) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Sigma") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          #strip.background.y = element_blank(),
          #strip.text.y = element_blank(),
          axis.title.x = element_blank())

(theta.arch.pc1 + alpha.arch.pc1 + sigma.arch.pc1) +
    plot_annotation(tag_levels = 'A')

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

## PC1 - Parameter differences

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r diffs_theta_ouwie_arch_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Archendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("arch.diff.theta.pc1.", gsub(" ", ".", agg.arch.diff.pc1$Group.1)), get)), format = "latex", caption = "Differences in Theta values for PC1 analysis of Architecture. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.arch, length(agg.arch.diff.pc1$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.arch.diff.pc1$Group.1), c(1, rep(length(states.arch), length(agg.arch.diff.pc1$Group.1)))))

```

```{r diffs_alpha_ouwie_arch_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Archendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("arch.diff.alpha.pc1.", gsub(" ", ".", agg.arch.diff.pc1$Group.1)), get)), format = "latex", caption = "Differences in Alpha values for PC1 analysis of Architecture. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.arch, length(agg.arch.diff.pc1$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.arch.diff.pc1$Group.1), c(1, rep(length(states.arch), length(agg.arch.diff.pc1$Group.1)))))

```

```{r diffs_sigma_ouwie_arch_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Archendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("arch.diff.sigma.pc1.", gsub(" ", ".", agg.arch.diff.pc1$Group.1)), get)), format = "latex", caption = "Differences in Sigma values for PC1 analysis of Architecture. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.arch, length(agg.arch.diff.pc1$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.arch.diff.pc1$Group.1), c(1, rep(length(states.arch), length(agg.arch.diff.pc1$Group.1)))))

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

# PC2 - Parameters

```{r results = 'asis', echo = FALSE}

if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}

```

```{r pars_ouwie_arch_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Archendage."}

theta.arch.plot.pc2 <- subset(theta.plot.pc2, disc.trait == "arch")
theta.arch.plot.pc2$variable <- as.character(theta.arch.plot.pc2$variable)
theta.arch.plot.pc2 <- theta.arch.plot.pc2[theta.arch.plot.pc2$value >= -10 & theta.arch.plot.pc2$value <= 10, ]

alpha.arch.plot.pc2 <- subset(alpha.plot.pc2, disc.trait == "arch")
alpha.arch.plot.pc2$variable <- as.character(alpha.arch.plot.pc2$variable)
alpha.arch.plot.pc2 <- alpha.arch.plot.pc2[alpha.arch.plot.pc2$value >= -10 & alpha.arch.plot.pc2$value <= 10, ]

sigma.arch.plot.pc2 <- subset(sigma.plot.pc2, disc.trait == "arch")
sigma.arch.plot.pc2$variable <- as.character(sigma.arch.plot.pc2$variable)
sigma.arch.plot.pc2 <- sigma.arch.plot.pc2[sigma.arch.plot.pc2$value >= -10 & sigma.arch.plot.pc2$value <= 10, ]

theta.arch.pc2 <-
    ggplot(na.omit(theta.arch.plot.pc2[-grep("3", theta.arch.plot.pc2$variable),])) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.arch) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

alpha.arch.pc2 <-
    ggplot(na.omit(alpha.arch.plot.pc2[-grep("3", alpha.arch.plot.pc2$variable),])) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.arch) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

sigma.arch.pc2 <-
    ggplot(na.omit(sigma.arch.plot.pc2[-grep("3", sigma.arch.plot.pc2$variable),])) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.arch) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Sigma") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          #strip.background.y = element_blank(),
          #strip.text.y = element_blank(),
          axis.title.x = element_blank())

(theta.arch.pc2 + alpha.arch.pc2 + sigma.arch.pc2) +
    plot_annotation(tag_levels = 'A')

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

## PC2 - Parameter differences

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r diffs_theta_ouwie_arch_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Archendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("arch.diff.theta.pc2.", gsub(" ", ".", agg.arch.diff.pc2$Group.1)), get)), format = "latex", caption = "Differences in Theta values for PC2 analysis of Architecture. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.arch, length(agg.arch.diff.pc2$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.arch.diff.pc1$Group.1), c(1, rep(length(states.arch), length(agg.arch.diff.pc1$Group.1)))))

```

```{r diffs_alpha_ouwie_arch_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Archendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("arch.diff.alpha.pc2.", gsub(" ", ".", agg.arch.diff.pc2$Group.1)), get)), format = "latex", caption = "Differences in Alpha values for PC2 analysis of Architecture. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.arch, length(agg.arch.diff.pc2$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.arch.diff.pc1$Group.1), c(1, rep(length(states.arch), length(agg.arch.diff.pc1$Group.1)))))

```

```{r diffs_sigma_ouwie_arch_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Archendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("arch.diff.sigma.pc2.", gsub(" ", ".", agg.arch.diff.pc2$Group.1)), get)), format = "latex", caption = "Differences in Sigma values for PC2 analysis of Architecture. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.arch, length(agg.arch.diff.pc2$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.arch.diff.pc1$Group.1), c(1, rep(length(states.arch), length(agg.arch.diff.pc1$Group.1)))))

```


```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

# PC3 - Parameters

```{r results = 'asis', echo = FALSE}

if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}

```

```{r pars_ouwie_arch_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Archendage."}

theta.arch.plot.pc3 <- subset(theta.plot.pc3, disc.trait == "arch")
theta.arch.plot.pc3$variable <- as.character(theta.arch.plot.pc3$variable)
theta.arch.plot.pc3 <- theta.arch.plot.pc3[theta.arch.plot.pc3$value >= -10 & theta.arch.plot.pc3$value <= 10, ]

alpha.arch.plot.pc3 <- subset(alpha.plot.pc3, disc.trait == "arch")
alpha.arch.plot.pc3$variable <- as.character(alpha.arch.plot.pc3$variable)
alpha.arch.plot.pc3 <- alpha.arch.plot.pc3[alpha.arch.plot.pc3$value >= -10 & alpha.arch.plot.pc3$value <= 10, ]

sigma.arch.plot.pc3 <- subset(sigma.plot.pc3, disc.trait == "arch")
sigma.arch.plot.pc3$variable <- as.character(sigma.arch.plot.pc3$variable)
sigma.arch.plot.pc3 <- sigma.arch.plot.pc3[sigma.arch.plot.pc3$value >= -10 & sigma.arch.plot.pc3$value <= 10, ]

theta.arch.pc3 <-
    ggplot(na.omit(theta.arch.plot.pc3[-grep("3", theta.arch.plot.pc3$variable),])) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.arch) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

alpha.arch.pc3 <-
    ggplot(na.omit(alpha.arch.plot.pc3[-grep("3", alpha.arch.plot.pc3$variable),])) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.arch) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

sigma.arch.pc3 <-
    ggplot(na.omit(sigma.arch.plot.pc3[-grep("3", sigma.arch.plot.pc3$variable),])) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.arch) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Sigma") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          #strip.background.y = element_blank(),
          #strip.text.y = element_blank(),
          axis.title.x = element_blank())

(theta.arch.pc3 + alpha.arch.pc3 + sigma.arch.pc3) +
    plot_annotation(tag_levels = 'A')

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

## PC3 - Parameter differences

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r diffs_theta_ouwie_arch_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Archendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("arch.diff.theta.pc3.", gsub(" ", ".", agg.arch.diff.pc3$Group.1)), get)), format = "latex", caption = "Differences in Theta values for PC3 analysis of Architecture. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.arch, length(agg.arch.diff.pc3$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.arch.diff.pc1$Group.1), c(1, rep(length(states.arch), length(agg.arch.diff.pc1$Group.1)))))

```

```{r diffs_alpha_ouwie_arch_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Archendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("arch.diff.alpha.pc3.", gsub(" ", ".", agg.arch.diff.pc3$Group.1)), get)), format = "latex", caption = "Differences in Alpha values for PC3 analysis of Architecture. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.arch, length(agg.arch.diff.pc3$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.arch.diff.pc1$Group.1), c(1, rep(length(states.arch), length(agg.arch.diff.pc1$Group.1)))))

```

```{r diffs_sigma_ouwie_arch_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Archendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("arch.diff.sigma.pc3.", gsub(" ", ".", agg.arch.diff.pc3$Group.1)), get)), format = "latex", caption = "Differences in Sigma values for PC3 analysis of Architecture. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.arch, length(agg.arch.diff.pc3$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.arch.diff.pc1$Group.1), c(1, rep(length(states.arch), length(agg.arch.diff.pc1$Group.1)))))

```


```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```







# Domatium Growth

# PC1 - Parameters

```{r results = 'asis', echo = FALSE}

if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}

```

```{r pars_ouwie_domgrow_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Domgrowendage."}

theta.domgrow.plot.pc1 <- subset(theta.plot.pc1, disc.trait == "domgrow")
theta.domgrow.plot.pc1$variable <- as.character(theta.domgrow.plot.pc1$variable)
theta.domgrow.plot.pc1 <- theta.domgrow.plot.pc1[theta.domgrow.plot.pc1$value >= -10 & theta.domgrow.plot.pc1$value <= 10, ]

alpha.domgrow.plot.pc1 <- subset(alpha.plot.pc1, disc.trait == "domgrow")
alpha.domgrow.plot.pc1$variable <- as.character(alpha.domgrow.plot.pc1$variable)
alpha.domgrow.plot.pc1 <- alpha.domgrow.plot.pc1[alpha.domgrow.plot.pc1$value >= -10 & alpha.domgrow.plot.pc1$value <= 10, ]

sigma.domgrow.plot.pc1 <- subset(sigma.plot.pc1, disc.trait == "domgrow")
sigma.domgrow.plot.pc1$variable <- as.character(sigma.domgrow.plot.pc1$variable)
sigma.domgrow.plot.pc1 <- sigma.domgrow.plot.pc1[sigma.domgrow.plot.pc1$value >= -10 & sigma.domgrow.plot.pc1$value <= 10, ]

theta.domgrow.pc1 <-
    ggplot(na.omit(theta.domgrow.plot.pc1)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.domgrow) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

alpha.domgrow.pc1 <-
    ggplot(na.omit(alpha.domgrow.plot.pc1)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.domgrow) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

sigma.domgrow.pc1 <-
    ggplot(na.omit(sigma.domgrow.plot.pc1)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.domgrow) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Sigma") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          #strip.background.y = element_blank(),
          #strip.text.y = element_blank(),
          axis.title.x = element_blank())

(theta.domgrow.pc1 + alpha.domgrow.pc1 + sigma.domgrow.pc1) +
    plot_annotation(tag_levels = 'A')

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

## PC1 - Parameter differences

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r diffs_theta_ouwie_domgrow_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Domgrowendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("domgrow.diff.theta.pc1.", gsub(" ", ".", agg.domgrow.diff.pc1$Group.1)), get)), format = "latex", caption = "Differences in Theta values for PC1 analysis of Domatium Growth. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.domgrow, length(agg.domgrow.diff.pc1$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.domgrow.diff.pc1$Group.1), c(1, rep(length(states.domgrow), length(agg.domgrow.diff.pc1$Group.1)))))

```

```{r diffs_alpha_ouwie_domgrow_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Domgrowendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("domgrow.diff.alpha.pc1.", gsub(" ", ".", agg.domgrow.diff.pc1$Group.1)), get)), format = "latex", caption = "Differences in Alpha values for PC1 analysis of Domatium Growth. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.domgrow, length(agg.domgrow.diff.pc1$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.domgrow.diff.pc1$Group.1), c(1, rep(length(states.domgrow), length(agg.domgrow.diff.pc1$Group.1)))))

```

```{r diffs_sigma_ouwie_domgrow_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Domgrowendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("domgrow.diff.sigma.pc1.", gsub(" ", ".", agg.domgrow.diff.pc1$Group.1)), get)), format = "latex", caption = "Differences in Sigma values for PC1 analysis of Domatium Growth. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.domgrow, length(agg.domgrow.diff.pc1$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.domgrow.diff.pc1$Group.1), c(1, rep(length(states.domgrow), length(agg.domgrow.diff.pc1$Group.1)))))

```


```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

# PC2 - Parameters

```{r results = 'asis', echo = FALSE}

if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}

```


```{r pars_ouwie_domgrow_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Domgrowendage."}

theta.domgrow.plot.pc2 <- subset(theta.plot.pc2, disc.trait == "domgrow")
theta.domgrow.plot.pc2$variable <- as.character(theta.domgrow.plot.pc2$variable)
theta.domgrow.plot.pc2 <- theta.domgrow.plot.pc2[theta.domgrow.plot.pc2$value >= -10 & theta.domgrow.plot.pc2$value <= 10, ]

alpha.domgrow.plot.pc2 <- subset(alpha.plot.pc2, disc.trait == "domgrow")
alpha.domgrow.plot.pc2$variable <- as.character(alpha.domgrow.plot.pc2$variable)
alpha.domgrow.plot.pc2 <- alpha.domgrow.plot.pc2[alpha.domgrow.plot.pc2$value >= -10 & alpha.domgrow.plot.pc2$value <= 10, ]

sigma.domgrow.plot.pc2 <- subset(sigma.plot.pc2, disc.trait == "domgrow")
sigma.domgrow.plot.pc2$variable <- as.character(sigma.domgrow.plot.pc2$variable)
sigma.domgrow.plot.pc2 <- sigma.domgrow.plot.pc2[sigma.domgrow.plot.pc2$value >= -10 & sigma.domgrow.plot.pc2$value <= 10, ]

theta.domgrow.pc2 <-
    ggplot(na.omit(theta.domgrow.plot.pc2[-grep("3", theta.domgrow.plot.pc2$variable),])) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.domgrow) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

alpha.domgrow.pc2 <-
    ggplot(na.omit(alpha.domgrow.plot.pc2[-grep("3", alpha.domgrow.plot.pc2$variable),])) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.domgrow) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

sigma.domgrow.pc2 <-
    ggplot(na.omit(sigma.domgrow.plot.pc2[-grep("3", sigma.domgrow.plot.pc2$variable),])) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.domgrow) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Sigma") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          #strip.background.y = element_blank(),
          #strip.text.y = element_blank(),
          axis.title.x = element_blank())

(theta.domgrow.pc2 + alpha.domgrow.pc2 + sigma.domgrow.pc2) +
    plot_annotation(tag_levels = 'A')

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

## PC2 - Parameter differences

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r diffs_theta_ouwie_domgrow_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Domgrowendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("domgrow.diff.theta.pc2.", gsub(" ", ".", agg.domgrow.diff.pc2$Group.1)), get)), format = "latex", caption = "Differences in Theta values for PC2 analysis of Domatium Growth. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.domgrow, length(agg.domgrow.diff.pc2$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.domgrow.diff.pc1$Group.1), c(1, rep(length(states.domgrow), length(agg.domgrow.diff.pc1$Group.1)))))

```

```{r diffs_alpha_ouwie_domgrow_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Domgrowendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("domgrow.diff.alpha.pc2.", gsub(" ", ".", agg.domgrow.diff.pc2$Group.1)), get)), format = "latex", caption = "Differences in Alpha values for PC2 analysis of Domatium Growth. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.domgrow, length(agg.domgrow.diff.pc2$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.domgrow.diff.pc1$Group.1), c(1, rep(length(states.domgrow), length(agg.domgrow.diff.pc1$Group.1)))))

```

```{r diffs_sigma_ouwie_domgrow_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Domgrowendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("domgrow.diff.sigma.pc2.", gsub(" ", ".", agg.domgrow.diff.pc2$Group.1)), get)), format = "latex", caption = "Differences in Sigma values for PC2 analysis of Domatium Growth. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.domgrow, length(agg.domgrow.diff.pc2$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.domgrow.diff.pc1$Group.1), c(1, rep(length(states.domgrow), length(agg.domgrow.diff.pc1$Group.1)))))

```


```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

# PC3 - Parameters

```{r results = 'asis', echo = FALSE}

if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}

```


```{r pars_ouwie_domgrow_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Domgrowendage."}

theta.domgrow.plot.pc3 <- subset(theta.plot.pc3, disc.trait == "domgrow")
theta.domgrow.plot.pc3$variable <- as.character(theta.domgrow.plot.pc3$variable)
theta.domgrow.plot.pc3 <- theta.domgrow.plot.pc3[theta.domgrow.plot.pc3$value >= -10 & theta.domgrow.plot.pc3$value <= 10, ]

alpha.domgrow.plot.pc3 <- subset(alpha.plot.pc3, disc.trait == "domgrow")
alpha.domgrow.plot.pc3$variable <- as.character(alpha.domgrow.plot.pc3$variable)
alpha.domgrow.plot.pc3 <- alpha.domgrow.plot.pc3[alpha.domgrow.plot.pc3$value >= -10 & alpha.domgrow.plot.pc3$value <= 10, ]

sigma.domgrow.plot.pc3 <- subset(sigma.plot.pc3, disc.trait == "domgrow")
sigma.domgrow.plot.pc3$variable <- as.character(sigma.domgrow.plot.pc3$variable)
sigma.domgrow.plot.pc3 <- sigma.domgrow.plot.pc3[sigma.domgrow.plot.pc3$value >= -10 & sigma.domgrow.plot.pc3$value <= 10, ]

theta.domgrow.pc3 <-
    ggplot(na.omit(theta.domgrow.plot.pc3[-grep("3", theta.domgrow.plot.pc3$variable),])) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.domgrow) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

alpha.domgrow.pc3 <-
    ggplot(na.omit(alpha.domgrow.plot.pc3[-grep("3", alpha.domgrow.plot.pc3$variable),])) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.domgrow) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

sigma.domgrow.pc3 <-
    ggplot(na.omit(sigma.domgrow.plot.pc3[-grep("3", sigma.domgrow.plot.pc3$variable),])) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.domgrow) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Sigma") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          #strip.background.y = element_blank(),
          #strip.text.y = element_blank(),
          axis.title.x = element_blank())

(theta.domgrow.pc3 + alpha.domgrow.pc3 + sigma.domgrow.pc3) +
    plot_annotation(tag_levels = 'A')

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

## PC3 - Parameter differences

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r diffs_theta_ouwie_domgrow_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Domgrowendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("domgrow.diff.theta.pc3.", gsub(" ", ".", agg.domgrow.diff.pc3$Group.1)), get)), format = "latex", caption = "Differences in Theta values for PC3 analysis of Domatium Growth. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.domgrow, length(agg.domgrow.diff.pc3$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.domgrow.diff.pc1$Group.1), c(1, rep(length(states.domgrow), length(agg.domgrow.diff.pc1$Group.1)))))

```

```{r diffs_alpha_ouwie_domgrow_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Domgrowendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("domgrow.diff.alpha.pc3.", gsub(" ", ".", agg.domgrow.diff.pc3$Group.1)), get)), format = "latex", caption = "Differences in Alpha values for PC3 analysis of Domatium Growth. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.domgrow, length(agg.domgrow.diff.pc3$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.domgrow.diff.pc1$Group.1), c(1, rep(length(states.domgrow), length(agg.domgrow.diff.pc1$Group.1)))))

```

```{r diffs_sigma_ouwie_domgrow_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Domgrowendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("domgrow.diff.sigma.pc3.", gsub(" ", ".", agg.domgrow.diff.pc3$Group.1)), get)), format = "latex", caption = "Differences in Sigma values for PC3 analysis of Domatium Growth. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.domgrow, length(agg.domgrow.diff.pc3$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.domgrow.diff.pc1$Group.1), c(1, rep(length(states.domgrow), length(agg.domgrow.diff.pc1$Group.1)))))

```


```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```






# Leaf Structure

# PC1 - Parameters

```{r results = 'asis', echo = FALSE}

if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}

```


```{r pars_ouwie_leafstruc_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Leafstrucendage."}

theta.leafstruc.plot.pc1 <- subset(theta.plot.pc1, disc.trait == "leafstruc")
theta.leafstruc.plot.pc1$variable <- as.character(theta.leafstruc.plot.pc1$variable)
theta.leafstruc.plot.pc1 <- theta.leafstruc.plot.pc1[theta.leafstruc.plot.pc1$value >= -10 & theta.leafstruc.plot.pc1$value <= 10, ]

alpha.leafstruc.plot.pc1 <- subset(alpha.plot.pc1, disc.trait == "leafstruc")
alpha.leafstruc.plot.pc1$variable <- as.character(alpha.leafstruc.plot.pc1$variable)
alpha.leafstruc.plot.pc1 <- alpha.leafstruc.plot.pc1[alpha.leafstruc.plot.pc1$value >= -10 & alpha.leafstruc.plot.pc1$value <= 10, ]

sigma.leafstruc.plot.pc1 <- subset(sigma.plot.pc1, disc.trait == "leafstruc")
sigma.leafstruc.plot.pc1$variable <- as.character(sigma.leafstruc.plot.pc1$variable)
sigma.leafstruc.plot.pc1 <- sigma.leafstruc.plot.pc1[sigma.leafstruc.plot.pc1$value >= -10 & sigma.leafstruc.plot.pc1$value <= 10, ]

theta.leafstruc.pc1 <-
    ggplot(na.omit(theta.leafstruc.plot.pc1)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.leafstruc) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

alpha.leafstruc.pc1 <-
    ggplot(na.omit(alpha.leafstruc.plot.pc1)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.leafstruc) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

sigma.leafstruc.pc1 <-
    ggplot(na.omit(sigma.leafstruc.plot.pc1)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.leafstruc) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Sigma") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          #strip.background.y = element_blank(),
          #strip.text.y = element_blank(),
          axis.title.x = element_blank())

(theta.leafstruc.pc1 + alpha.leafstruc.pc1 + sigma.leafstruc.pc1) +
    plot_annotation(tag_levels = 'A')

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

## PC1 - Parameter differences

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r diffs_theta_ouwie_leafstruc_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Leafstrucendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("leafstruc.diff.theta.pc1.", gsub(" ", ".", agg.leafstruc.diff.pc1$Group.1)), get)), format = "latex", caption = "Differences in Theta values for PC1 analysis of Leaf Structure. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.leafstruc, length(agg.leafstruc.diff.pc1$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.leafstruc.diff.pc1$Group.1), c(1, rep(length(states.leafstruc), length(agg.leafstruc.diff.pc1$Group.1)))))

```

```{r diffs_alpha_ouwie_leafstruc_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Leafstrucendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("leafstruc.diff.alpha.pc1.", gsub(" ", ".", agg.leafstruc.diff.pc1$Group.1)), get)), format = "latex", caption = "Differences in Alpha values for PC1 analysis of Leaf Structure. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.leafstruc, length(agg.leafstruc.diff.pc1$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.leafstruc.diff.pc1$Group.1), c(1, rep(length(states.leafstruc), length(agg.leafstruc.diff.pc1$Group.1)))))

```

```{r diffs_sigma_ouwie_leafstruc_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Leafstrucendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("leafstruc.diff.sigma.pc1.", gsub(" ", ".", agg.leafstruc.diff.pc1$Group.1)), get)), format = "latex", caption = "Differences in Sigma values for PC1 analysis of Leaf Structure. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.leafstruc, length(agg.leafstruc.diff.pc1$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.leafstruc.diff.pc1$Group.1), c(1, rep(length(states.leafstruc), length(agg.leafstruc.diff.pc1$Group.1)))))

```


```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

# PC2 - Parameters

```{r results = 'asis', echo = FALSE}

if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}

```

```{r pars_ouwie_leafstruc_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Leafstrucendage."}

theta.leafstruc.plot.pc2 <- subset(theta.plot.pc2, disc.trait == "leafstruc")
theta.leafstruc.plot.pc2$variable <- as.character(theta.leafstruc.plot.pc2$variable)
theta.leafstruc.plot.pc2 <- theta.leafstruc.plot.pc2[theta.leafstruc.plot.pc2$value >= -10 & theta.leafstruc.plot.pc2$value <= 10, ]

alpha.leafstruc.plot.pc2 <- subset(alpha.plot.pc2, disc.trait == "leafstruc")
alpha.leafstruc.plot.pc2$variable <- as.character(alpha.leafstruc.plot.pc2$variable)
alpha.leafstruc.plot.pc2 <- alpha.leafstruc.plot.pc2[alpha.leafstruc.plot.pc2$value >= -10 & alpha.leafstruc.plot.pc2$value <= 10, ]

sigma.leafstruc.plot.pc2 <- subset(sigma.plot.pc2, disc.trait == "leafstruc")
sigma.leafstruc.plot.pc2$variable <- as.character(sigma.leafstruc.plot.pc2$variable)
sigma.leafstruc.plot.pc2 <- sigma.leafstruc.plot.pc2[sigma.leafstruc.plot.pc2$value >= -10 & sigma.leafstruc.plot.pc2$value <= 10, ]

theta.leafstruc.pc2 <-
    ggplot(na.omit(theta.leafstruc.plot.pc2)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.leafstruc) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

alpha.leafstruc.pc2 <-
    ggplot(na.omit(alpha.leafstruc.plot.pc2)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.leafstruc) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

sigma.leafstruc.pc2 <-
    ggplot(na.omit(sigma.leafstruc.plot.pc2)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.leafstruc) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Sigma") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          #strip.background.y = element_blank(),
          #strip.text.y = element_blank(),
          axis.title.x = element_blank())

(theta.leafstruc.pc2 + alpha.leafstruc.pc2 + sigma.leafstruc.pc2) +
    plot_annotation(tag_levels = 'A')

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

## PC2 - Parameter differences

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r diffs_theta_ouwie_leafstruc_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Leafstrucendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("leafstruc.diff.theta.pc2.", gsub(" ", ".", agg.leafstruc.diff.pc2$Group.1)), get)), format = "latex", caption = "Differences in Theta values for PC2 analysis of Leaf Structure. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.leafstruc, length(agg.leafstruc.diff.pc2$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.leafstruc.diff.pc1$Group.1), c(1, rep(length(states.leafstruc), length(agg.leafstruc.diff.pc1$Group.1)))))

```

```{r diffs_alpha_ouwie_leafstruc_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Leafstrucendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("leafstruc.diff.alpha.pc2.", gsub(" ", ".", agg.leafstruc.diff.pc2$Group.1)), get)), format = "latex", caption = "Differences in Alpha values for PC2 analysis of Leaf Structure. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.leafstruc, length(agg.leafstruc.diff.pc2$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.leafstruc.diff.pc1$Group.1), c(1, rep(length(states.leafstruc), length(agg.leafstruc.diff.pc1$Group.1)))))

```

```{r diffs_sigma_ouwie_leafstruc_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Leafstrucendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("leafstruc.diff.sigma.pc2.", gsub(" ", ".", agg.leafstruc.diff.pc2$Group.1)), get)), format = "latex", caption = "Differences in Sigma values for PC2 analysis of Leaf Structure. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.leafstruc, length(agg.leafstruc.diff.pc2$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.leafstruc.diff.pc1$Group.1), c(1, rep(length(states.leafstruc), length(agg.leafstruc.diff.pc1$Group.1)))))

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

# PC3 - Parameters

```{r results = 'asis', echo = FALSE}

if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}

```

```{r pars_ouwie_leafstruc_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Leafstrucendage."}

theta.leafstruc.plot.pc3 <- subset(theta.plot.pc3, disc.trait == "leafstruc")
theta.leafstruc.plot.pc3$variable <- as.character(theta.leafstruc.plot.pc3$variable)
theta.leafstruc.plot.pc3 <- theta.leafstruc.plot.pc3[theta.leafstruc.plot.pc3$value >= -10 & theta.leafstruc.plot.pc3$value <= 10, ]

alpha.leafstruc.plot.pc3 <- subset(alpha.plot.pc3, disc.trait == "leafstruc")
alpha.leafstruc.plot.pc3$variable <- as.character(alpha.leafstruc.plot.pc3$variable)
alpha.leafstruc.plot.pc3 <- alpha.leafstruc.plot.pc3[alpha.leafstruc.plot.pc3$value >= -10 & alpha.leafstruc.plot.pc3$value <= 10, ]

sigma.leafstruc.plot.pc3 <- subset(sigma.plot.pc3, disc.trait == "leafstruc")
sigma.leafstruc.plot.pc3$variable <- as.character(sigma.leafstruc.plot.pc3$variable)
sigma.leafstruc.plot.pc3 <- sigma.leafstruc.plot.pc3[sigma.leafstruc.plot.pc3$value >= -10 & sigma.leafstruc.plot.pc3$value <= 10, ]

theta.leafstruc.pc3 <-
    ggplot(na.omit(theta.leafstruc.plot.pc3)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.leafstruc) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

alpha.leafstruc.pc3 <-
    ggplot(na.omit(alpha.leafstruc.plot.pc3)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.leafstruc) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

sigma.leafstruc.pc3 <-
    ggplot(na.omit(sigma.leafstruc.plot.pc3)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.leafstruc) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Sigma") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          #strip.background.y = element_blank(),
          #strip.text.y = element_blank(),
          axis.title.x = element_blank())

(theta.leafstruc.pc3 + alpha.leafstruc.pc3 + sigma.leafstruc.pc3) +
    plot_annotation(tag_levels = 'A')

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

## PC3 - Parameter differences

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r diffs_theta_ouwie_leafstruc_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Leafstrucendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("leafstruc.diff.theta.pc3.", gsub(" ", ".", agg.leafstruc.diff.pc3$Group.1)), get)), format = "latex", caption = "Differences in Theta values for PC3 analysis of Leaf Structure. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.leafstruc, length(agg.leafstruc.diff.pc3$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.leafstruc.diff.pc1$Group.1), c(1, rep(length(states.leafstruc), length(agg.leafstruc.diff.pc1$Group.1)))))

```

```{r diffs_alpha_ouwie_leafstruc_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Leafstrucendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("leafstruc.diff.alpha.pc3.", gsub(" ", ".", agg.leafstruc.diff.pc3$Group.1)), get)), format = "latex", caption = "Differences in Alpha values for PC3 analysis of Leaf Structure. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.leafstruc, length(agg.leafstruc.diff.pc3$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.leafstruc.diff.pc1$Group.1), c(1, rep(length(states.leafstruc), length(agg.leafstruc.diff.pc1$Group.1)))))

```

```{r diffs_sigma_ouwie_leafstruc_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Leafstrucendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("leafstruc.diff.sigma.pc3.", gsub(" ", ".", agg.leafstruc.diff.pc3$Group.1)), get)), format = "latex", caption = "Differences in Sigma values for PC3 analysis of Leaf Structure. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.leafstruc, length(agg.leafstruc.diff.pc3$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.leafstruc.diff.pc1$Group.1), c(1, rep(length(states.leafstruc), length(agg.leafstruc.diff.pc1$Group.1)))))

```


```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```






# Mating System

# PC1 - Parameters

```{r results = 'asis', echo = FALSE}

if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}

```

```{r pars_ouwie_matsys_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Matsysendage."}

theta.matsys.plot.pc1 <- subset(theta.plot.pc1, disc.trait == "matsys")
theta.matsys.plot.pc1$variable <- as.character(theta.matsys.plot.pc1$variable)
theta.matsys.plot.pc1 <- theta.matsys.plot.pc1[theta.matsys.plot.pc1$value >= -10 & theta.matsys.plot.pc1$value <= 10, ]

alpha.matsys.plot.pc1 <- subset(alpha.plot.pc1, disc.trait == "matsys")
alpha.matsys.plot.pc1$variable <- as.character(alpha.matsys.plot.pc1$variable)
alpha.matsys.plot.pc1 <- alpha.matsys.plot.pc1[alpha.matsys.plot.pc1$value >= -10 & alpha.matsys.plot.pc1$value <= 10, ]

sigma.matsys.plot.pc1 <- subset(sigma.plot.pc1, disc.trait == "matsys")
sigma.matsys.plot.pc1$variable <- as.character(sigma.matsys.plot.pc1$variable)
sigma.matsys.plot.pc1 <- sigma.matsys.plot.pc1[sigma.matsys.plot.pc1$value >= -10 & sigma.matsys.plot.pc1$value <= 10, ]

theta.matsys.pc1 <-
    ggplot(na.omit(theta.matsys.plot.pc1)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.matsys) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

alpha.matsys.pc1 <-
    ggplot(na.omit(alpha.matsys.plot.pc1)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.matsys) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

sigma.matsys.pc1 <-
    ggplot(na.omit(sigma.matsys.plot.pc1)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.matsys) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Sigma") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          #strip.background.y = element_blank(),
          #strip.text.y = element_blank(),
          axis.title.x = element_blank())

(theta.matsys.pc1 + alpha.matsys.pc1 + sigma.matsys.pc1) +
    plot_annotation(tag_levels = 'A')

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

## PC1 - Parameter differences

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r diffs_theta_ouwie_matsys_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Matsysendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("matsys.diff.theta.pc1.", gsub(" ", ".", agg.matsys.diff.pc1$Group.1)), get)), format = "latex", caption = "Differences in Theta values for PC1 analysis of Mating System. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.matsys, length(agg.matsys.diff.pc1$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.matsys.diff.pc1$Group.1), c(1, rep(length(states.matsys), length(agg.matsys.diff.pc1$Group.1)))))

```

```{r diffs_alpha_ouwie_matsys_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Matsysendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("matsys.diff.alpha.pc1.", gsub(" ", ".", agg.matsys.diff.pc1$Group.1)), get)), format = "latex", caption = "Differences in Alpha values for PC1 analysis of Mating System. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.matsys, length(agg.matsys.diff.pc1$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.matsys.diff.pc1$Group.1), c(1, rep(length(states.matsys), length(agg.matsys.diff.pc1$Group.1)))))

```

```{r diffs_sigma_ouwie_matsys_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Matsysendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("matsys.diff.sigma.pc1.", gsub(" ", ".", agg.matsys.diff.pc1$Group.1)), get)), format = "latex", caption = "Differences in Sigma values for PC1 analysis of Mating System. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.matsys, length(agg.matsys.diff.pc1$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.matsys.diff.pc1$Group.1), c(1, rep(length(states.matsys), length(agg.matsys.diff.pc1$Group.1)))))

```


```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

# PC2 - Parameters

```{r results = 'asis', echo = FALSE}

if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}

```

```{r pars_ouwie_matsys_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Matsysendage."}

theta.matsys.plot.pc2 <- subset(theta.plot.pc2, disc.trait == "matsys")
theta.matsys.plot.pc2$variable <- as.character(theta.matsys.plot.pc2$variable)
theta.matsys.plot.pc2 <- theta.matsys.plot.pc2[theta.matsys.plot.pc2$value >= -10 & theta.matsys.plot.pc2$value <= 10, ]

alpha.matsys.plot.pc2 <- subset(alpha.plot.pc2, disc.trait == "matsys")
alpha.matsys.plot.pc2$variable <- as.character(alpha.matsys.plot.pc2$variable)
alpha.matsys.plot.pc2 <- alpha.matsys.plot.pc2[alpha.matsys.plot.pc2$value >= -10 & alpha.matsys.plot.pc2$value <= 10, ]

sigma.matsys.plot.pc2 <- subset(sigma.plot.pc2, disc.trait == "matsys")
sigma.matsys.plot.pc2$variable <- as.character(sigma.matsys.plot.pc2$variable)
sigma.matsys.plot.pc2 <- sigma.matsys.plot.pc2[sigma.matsys.plot.pc2$value >= -10 & sigma.matsys.plot.pc2$value <= 10, ]

theta.matsys.pc2 <-
    ggplot(na.omit(theta.matsys.plot.pc2)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.matsys) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

alpha.matsys.pc2 <-
    ggplot(na.omit(alpha.matsys.plot.pc2)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.matsys) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

sigma.matsys.pc2 <-
    ggplot(na.omit(sigma.matsys.plot.pc2)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.matsys) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Sigma") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          #strip.background.y = element_blank(),
          #strip.text.y = element_blank(),
          axis.title.x = element_blank())

(theta.matsys.pc2 + alpha.matsys.pc2 + sigma.matsys.pc2) +
    plot_annotation(tag_levels = 'A')

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

## PC2 - Parameter differences

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r diffs_theta_ouwie_matsys_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Matsysendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("matsys.diff.theta.pc2.", gsub(" ", ".", agg.matsys.diff.pc2$Group.1)), get)), format = "latex", caption = "Differences in Theta values for PC2 analysis of Mating System. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.matsys, length(agg.matsys.diff.pc2$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.matsys.diff.pc1$Group.1), c(1, rep(length(states.matsys), length(agg.matsys.diff.pc1$Group.1)))))

```

```{r diffs_alpha_ouwie_matsys_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Matsysendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("matsys.diff.alpha.pc2.", gsub(" ", ".", agg.matsys.diff.pc2$Group.1)), get)), format = "latex", caption = "Differences in Alpha values for PC2 analysis of Mating System. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.matsys, length(agg.matsys.diff.pc2$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.matsys.diff.pc1$Group.1), c(1, rep(length(states.matsys), length(agg.matsys.diff.pc1$Group.1)))))

```

```{r diffs_sigma_ouwie_matsys_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Matsysendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("matsys.diff.sigma.pc2.", gsub(" ", ".", agg.matsys.diff.pc2$Group.1)), get)), format = "latex", caption = "Differences in Sigma values for PC2 analysis of Mating System. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.matsys, length(agg.matsys.diff.pc2$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.matsys.diff.pc1$Group.1), c(1, rep(length(states.matsys), length(agg.matsys.diff.pc1$Group.1)))))

```


```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

# PC3 - Parameters

```{r results = 'asis', echo = FALSE}

if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}

```

```{r pars_ouwie_matsys_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Matsysendage."}

theta.matsys.plot.pc3 <- subset(theta.plot.pc3, disc.trait == "matsys")
theta.matsys.plot.pc3$variable <- as.character(theta.matsys.plot.pc3$variable)
theta.matsys.plot.pc3 <- theta.matsys.plot.pc3[theta.matsys.plot.pc3$value >= -10 & theta.matsys.plot.pc3$value <= 10, ]

alpha.matsys.plot.pc3 <- subset(alpha.plot.pc3, disc.trait == "matsys")
alpha.matsys.plot.pc3$variable <- as.character(alpha.matsys.plot.pc3$variable)
alpha.matsys.plot.pc3 <- alpha.matsys.plot.pc3[alpha.matsys.plot.pc3$value >= -10 & alpha.matsys.plot.pc3$value <= 10, ]

sigma.matsys.plot.pc3 <- subset(sigma.plot.pc3, disc.trait == "matsys")
sigma.matsys.plot.pc3$variable <- as.character(sigma.matsys.plot.pc3$variable)
sigma.matsys.plot.pc3 <- sigma.matsys.plot.pc3[sigma.matsys.plot.pc3$value >= -10 & sigma.matsys.plot.pc3$value <= 10, ]

theta.matsys.pc3 <-
    ggplot(na.omit(theta.matsys.plot.pc3)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.matsys) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

alpha.matsys.pc3 <-
    ggplot(na.omit(alpha.matsys.plot.pc3)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.matsys) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

sigma.matsys.pc3 <-
    ggplot(na.omit(sigma.matsys.plot.pc3)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.matsys) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Sigma") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          #strip.background.y = element_blank(),
          #strip.text.y = element_blank(),
          axis.title.x = element_blank())

(theta.matsys.pc3 + alpha.matsys.pc3 + sigma.matsys.pc3) +
    plot_annotation(tag_levels = 'A')

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

## PC3 - Parameter differences

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r diffs_theta_ouwie_matsys_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Matsysendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("matsys.diff.theta.pc3.", gsub(" ", ".", agg.matsys.diff.pc3$Group.1)), get)), format = "latex", caption = "Differences in Theta values for PC3 analysis of Mating System. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.matsys, length(agg.matsys.diff.pc3$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.matsys.diff.pc1$Group.1), c(1, rep(length(states.matsys), length(agg.matsys.diff.pc1$Group.1)))))

```

```{r diffs_alpha_ouwie_matsys_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Matsysendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("matsys.diff.alpha.pc3.", gsub(" ", ".", agg.matsys.diff.pc3$Group.1)), get)), format = "latex", caption = "Differences in Alpha values for PC3 analysis of Mating System. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.matsys, length(agg.matsys.diff.pc3$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.matsys.diff.pc1$Group.1), c(1, rep(length(states.matsys), length(agg.matsys.diff.pc1$Group.1)))))

```

```{r diffs_sigma_ouwie_matsys_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Matsysendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("matsys.diff.sigma.pc3.", gsub(" ", ".", agg.matsys.diff.pc3$Group.1)), get)), format = "latex", caption = "Differences in Sigma values for PC3 analysis of Mating System. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.matsys, length(agg.matsys.diff.pc3$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.matsys.diff.pc1$Group.1), c(1, rep(length(states.matsys), length(agg.matsys.diff.pc1$Group.1)))))

```


```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```






# Reward

# PC1 - Parameters

```{r results = 'asis', echo = FALSE}

if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}

```

```{r pars_ouwie_reward_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Rewardendage."}

theta.reward.plot.pc1 <- subset(theta.plot.pc1, disc.trait == "reward")
theta.reward.plot.pc1$variable <- as.character(theta.reward.plot.pc1$variable)
theta.reward.plot.pc1 <- theta.reward.plot.pc1[theta.reward.plot.pc1$value >= -10 & theta.reward.plot.pc1$value <= 10, ]

alpha.reward.plot.pc1 <- subset(alpha.plot.pc1, disc.trait == "reward")
alpha.reward.plot.pc1$variable <- as.character(alpha.reward.plot.pc1$variable)
alpha.reward.plot.pc1 <- alpha.reward.plot.pc1[alpha.reward.plot.pc1$value >= -10 & alpha.reward.plot.pc1$value <= 10, ]

sigma.reward.plot.pc1 <- subset(sigma.plot.pc1, disc.trait == "reward")
sigma.reward.plot.pc1$variable <- as.character(sigma.reward.plot.pc1$variable)
sigma.reward.plot.pc1 <- sigma.reward.plot.pc1[sigma.reward.plot.pc1$value >= -10 & sigma.reward.plot.pc1$value <= 10, ]

theta.reward.pc1 <-
    ggplot(na.omit(theta.reward.plot.pc1)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.reward) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

alpha.reward.pc1 <-
    ggplot(na.omit(alpha.reward.plot.pc1)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.reward) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

sigma.reward.pc1 <-
    ggplot(na.omit(sigma.reward.plot.pc1)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.reward) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Sigma") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          #strip.background.y = element_blank(),
          #strip.text.y = element_blank(),
          axis.title.x = element_blank())

(theta.reward.pc1 + alpha.reward.pc1 + sigma.reward.pc1) +
    plot_annotation(tag_levels = 'A')

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

## PC1 - Parameter differences

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r diffs_theta_ouwie_reward_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Rewardendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("reward.diff.theta.pc1.", gsub(" ", ".", agg.reward.diff.pc1$Group.1)), get)), format = "latex", caption = "Differences in Theta values for PC1 analysis of Reward. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.reward, length(agg.reward.diff.pc1$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.reward.diff.pc1$Group.1), c(1, rep(length(states.reward), length(agg.reward.diff.pc1$Group.1)))))

```

```{r diffs_alpha_ouwie_reward_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Rewardendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("reward.diff.alpha.pc1.", gsub(" ", ".", agg.reward.diff.pc1$Group.1)), get)), format = "latex", caption = "Differences in Alpha values for PC1 analysis of Reward. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.reward, length(agg.reward.diff.pc1$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.reward.diff.pc1$Group.1), c(1, rep(length(states.reward), length(agg.reward.diff.pc1$Group.1)))))

```

```{r diffs_sigma_ouwie_reward_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Rewardendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("reward.diff.sigma.pc1.", gsub(" ", ".", agg.reward.diff.pc1$Group.1)), get)), format = "latex", caption = "Differences in Sigma values for PC1 analysis of Reward. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.reward, length(agg.reward.diff.pc1$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.reward.diff.pc1$Group.1), c(1, rep(length(states.reward), length(agg.reward.diff.pc1$Group.1)))))

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

# PC2 - Parameter

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r pars_ouwie_reward_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Rewardendage."}

theta.reward.plot.pc2 <- subset(theta.plot.pc2, disc.trait == "reward")
theta.reward.plot.pc2$variable <- as.character(theta.reward.plot.pc2$variable)
theta.reward.plot.pc2 <- theta.reward.plot.pc2[theta.reward.plot.pc2$value >= -10 & theta.reward.plot.pc2$value <= 10, ]

alpha.reward.plot.pc2 <- subset(alpha.plot.pc2, disc.trait == "reward")
alpha.reward.plot.pc2$variable <- as.character(alpha.reward.plot.pc2$variable)
alpha.reward.plot.pc2 <- alpha.reward.plot.pc2[alpha.reward.plot.pc2$value >= -10 & alpha.reward.plot.pc2$value <= 10, ]

sigma.reward.plot.pc2 <- subset(sigma.plot.pc2, disc.trait == "reward")
sigma.reward.plot.pc2$variable <- as.character(sigma.reward.plot.pc2$variable)
sigma.reward.plot.pc2 <- sigma.reward.plot.pc2[sigma.reward.plot.pc2$value >= -10 & sigma.reward.plot.pc2$value <= 10, ]

theta.reward.pc2 <-
    ggplot(na.omit(theta.reward.plot.pc2)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.reward) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

alpha.reward.pc2 <-
    ggplot(na.omit(alpha.reward.plot.pc2)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.reward) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

sigma.reward.pc2 <-
    ggplot(na.omit(sigma.reward.plot.pc2)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.reward) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Sigma") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          #strip.background.y = element_blank(),
          #strip.text.y = element_blank(),
          axis.title.x = element_blank())

(theta.reward.pc2 + alpha.reward.pc2 + sigma.reward.pc2) +
    plot_annotation(tag_levels = 'A')

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

## PC2 - Parameter differences

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r diffs_theta_ouwie_reward_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Rewardendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("reward.diff.theta.pc2.", gsub(" ", ".", agg.reward.diff.pc2$Group.1)), get)), format = "latex", caption = "Differences in Theta values for PC2 analysis of Reward. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.reward, length(agg.reward.diff.pc2$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.reward.diff.pc1$Group.1), c(1, rep(length(states.reward), length(agg.reward.diff.pc1$Group.1)))))

```

```{r diffs_alpha_ouwie_reward_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Rewardendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("reward.diff.alpha.pc2.", gsub(" ", ".", agg.reward.diff.pc2$Group.1)), get)), format = "latex", caption = "Differences in Alpha values for PC2 analysis of Reward. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.reward, length(agg.reward.diff.pc2$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.reward.diff.pc1$Group.1), c(1, rep(length(states.reward), length(agg.reward.diff.pc1$Group.1)))))

```

```{r diffs_sigma_ouwie_reward_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Rewardendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("reward.diff.sigma.pc2.", gsub(" ", ".", agg.reward.diff.pc2$Group.1)), get)), format = "latex", caption = "Differences in Sigma values for PC2 analysis of Reward. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.reward, length(agg.reward.diff.pc2$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.reward.diff.pc1$Group.1), c(1, rep(length(states.reward), length(agg.reward.diff.pc1$Group.1)))))

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

# PC3 - Parameters

```{r results = 'asis', echo = FALSE}

if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}

```


```{r pars_ouwie_reward_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Rewardendage."}

theta.reward.plot.pc3 <- subset(theta.plot.pc3, disc.trait == "reward")
theta.reward.plot.pc3$variable <- as.character(theta.reward.plot.pc3$variable)
theta.reward.plot.pc3 <- theta.reward.plot.pc3[theta.reward.plot.pc3$value >= -10 & theta.reward.plot.pc3$value <= 10, ]

alpha.reward.plot.pc3 <- subset(alpha.plot.pc3, disc.trait == "reward")
alpha.reward.plot.pc3$variable <- as.character(alpha.reward.plot.pc3$variable)
alpha.reward.plot.pc3 <- alpha.reward.plot.pc3[alpha.reward.plot.pc3$value >= -10 & alpha.reward.plot.pc3$value <= 10, ]

sigma.reward.plot.pc3 <- subset(sigma.plot.pc3, disc.trait == "reward")
sigma.reward.plot.pc3$variable <- as.character(sigma.reward.plot.pc3$variable)
sigma.reward.plot.pc3 <- sigma.reward.plot.pc3[sigma.reward.plot.pc3$value >= -10 & sigma.reward.plot.pc3$value <= 10, ]

theta.reward.pc3 <-
    ggplot(na.omit(theta.reward.plot.pc3)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.reward) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

alpha.reward.pc3 <-
    ggplot(na.omit(alpha.reward.plot.pc3)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.reward) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

sigma.reward.pc3 <-
    ggplot(na.omit(sigma.reward.plot.pc3)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.reward) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Sigma") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          #strip.background.y = element_blank(),
          #strip.text.y = element_blank(),
          axis.title.x = element_blank())

(theta.reward.pc3 + alpha.reward.pc3 + sigma.reward.pc3) +
    plot_annotation(tag_levels = 'A')

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

## PC3 - Parameter differences

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r diffs_theta_ouwie_reward_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Rewardendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("reward.diff.theta.pc3.", gsub(" ", ".", agg.reward.diff.pc3$Group.1)), get)), format = "latex", caption = "Differences in Theta values for PC3 analysis of Reward. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.reward, length(agg.reward.diff.pc3$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.reward.diff.pc1$Group.1), c(1, rep(length(states.reward), length(agg.reward.diff.pc1$Group.1)))))

```

```{r diffs_alpha_ouwie_reward_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Rewardendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("reward.diff.alpha.pc3.", gsub(" ", ".", agg.reward.diff.pc3$Group.1)), get)), format = "latex", caption = "Differences in Alpha values for PC3 analysis of Reward. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.reward, length(agg.reward.diff.pc3$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.reward.diff.pc1$Group.1), c(1, rep(length(states.reward), length(agg.reward.diff.pc1$Group.1)))))

```

```{r diffs_sigma_ouwie_reward_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Rewardendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("reward.diff.sigma.pc3.", gsub(" ", ".", agg.reward.diff.pc3$Group.1)), get)), format = "latex", caption = "Differences in Sigma values for PC3 analysis of Reward. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.reward, length(agg.reward.diff.pc3$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.reward.diff.pc1$Group.1), c(1, rep(length(states.reward), length(agg.reward.diff.pc1$Group.1)))))

```


```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```





# Strategy

# PC1 - Parameters

```{r results = 'asis', echo = FALSE}

if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}

```


```{r pars_ouwie_strategy_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Strategyendage."}

theta.strategy.plot.pc1 <- subset(theta.plot.pc1, disc.trait == "strategy")
theta.strategy.plot.pc1$variable <- as.character(theta.strategy.plot.pc1$variable)
theta.strategy.plot.pc1 <- theta.strategy.plot.pc1[theta.strategy.plot.pc1$value >= -10 & theta.strategy.plot.pc1$value <= 10, ]

alpha.strategy.plot.pc1 <- subset(alpha.plot.pc1, disc.trait == "strategy")
alpha.strategy.plot.pc1$variable <- as.character(alpha.strategy.plot.pc1$variable)
alpha.strategy.plot.pc1 <- alpha.strategy.plot.pc1[alpha.strategy.plot.pc1$value >= -10 & alpha.strategy.plot.pc1$value <= 10, ]

sigma.strategy.plot.pc1 <- subset(sigma.plot.pc1, disc.trait == "strategy")
sigma.strategy.plot.pc1$variable <- as.character(sigma.strategy.plot.pc1$variable)
sigma.strategy.plot.pc1 <- sigma.strategy.plot.pc1[sigma.strategy.plot.pc1$value >= -10 & sigma.strategy.plot.pc1$value <= 10, ]

theta.strategy.pc1 <-
    ggplot(na.omit(theta.strategy.plot.pc1)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.strategy) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

alpha.strategy.pc1 <-
    ggplot(na.omit(alpha.strategy.plot.pc1)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.strategy) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

sigma.strategy.pc1 <-
    ggplot(na.omit(sigma.strategy.plot.pc1)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.strategy) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Sigma") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          #strip.background.y = element_blank(),
          #strip.text.y = element_blank(),
          axis.title.x = element_blank())

(theta.strategy.pc1 + alpha.strategy.pc1 + sigma.strategy.pc1) +
    plot_annotation(tag_levels = 'A')

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

## PC1 - Parameter differences

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r diffs_theta_ouwie_strategy_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Strategyendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("strategy.diff.theta.pc1.", gsub(" ", ".", agg.strategy.diff.pc1$Group.1)), get)), format = "latex", caption = "Differences in Theta values for PC1 analysis of Strategy. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.strategy, length(agg.strategy.diff.pc1$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.strategy.diff.pc1$Group.1), c(1, rep(length(states.strategy), length(agg.strategy.diff.pc1$Group.1)))))

```

```{r diffs_alpha_ouwie_strategy_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Strategyendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("strategy.diff.alpha.pc1.", gsub(" ", ".", agg.strategy.diff.pc1$Group.1)), get)), format = "latex", caption = "Differences in Alpha values for PC1 analysis of Strategy. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.strategy, length(agg.strategy.diff.pc1$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.strategy.diff.pc1$Group.1), c(1, rep(length(states.strategy), length(agg.strategy.diff.pc1$Group.1)))))

```

```{r diffs_sigma_ouwie_strategy_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Strategyendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("strategy.diff.sigma.pc1.", gsub(" ", ".", agg.strategy.diff.pc1$Group.1)), get)), format = "latex", caption = "Differences in Sigma values for PC1 analysis of Strategy. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.strategy, length(agg.strategy.diff.pc1$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.strategy.diff.pc1$Group.1), c(1, rep(length(states.strategy), length(agg.strategy.diff.pc1$Group.1)))))

```


```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

# PC2 - Parameters

```{r results = 'asis', echo = FALSE}

if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}

```


```{r pars_ouwie_strategy_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Strategyendage."}

theta.strategy.plot.pc2 <- subset(theta.plot.pc2, disc.trait == "strategy")
theta.strategy.plot.pc2$variable <- as.character(theta.strategy.plot.pc2$variable)
theta.strategy.plot.pc2 <- theta.strategy.plot.pc2[theta.strategy.plot.pc2$value >= -10 & theta.strategy.plot.pc2$value <= 10, ]

alpha.strategy.plot.pc2 <- subset(alpha.plot.pc2, disc.trait == "strategy")
alpha.strategy.plot.pc2$variable <- as.character(alpha.strategy.plot.pc2$variable)
alpha.strategy.plot.pc2 <- alpha.strategy.plot.pc2[alpha.strategy.plot.pc2$value >= -10 & alpha.strategy.plot.pc2$value <= 10, ]

sigma.strategy.plot.pc2 <- subset(sigma.plot.pc2, disc.trait == "strategy")
sigma.strategy.plot.pc2$variable <- as.character(sigma.strategy.plot.pc2$variable)
sigma.strategy.plot.pc2 <- sigma.strategy.plot.pc2[sigma.strategy.plot.pc2$value >= -10 & sigma.strategy.plot.pc2$value <= 10, ]

theta.strategy.pc2 <-
    ggplot(na.omit(theta.strategy.plot.pc2)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.strategy) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

alpha.strategy.pc2 <-
    ggplot(na.omit(alpha.strategy.plot.pc2)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.strategy) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

sigma.strategy.pc2 <-
    ggplot(na.omit(sigma.strategy.plot.pc2)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.strategy) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Sigma") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          #strip.background.y = element_blank(),
          #strip.text.y = element_blank(),
          axis.title.x = element_blank())

(theta.strategy.pc2 + alpha.strategy.pc2 + sigma.strategy.pc2) +
    plot_annotation(tag_levels = 'A')

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

## PC2 - Parameter differences

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r diffs_theta_ouwie_strategy_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Strategyendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("strategy.diff.theta.pc2.", gsub(" ", ".", agg.strategy.diff.pc2$Group.1)), get)), format = "latex", caption = "Differences in Theta values for PC2 analysis of Strategy. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.strategy, length(agg.strategy.diff.pc2$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.strategy.diff.pc1$Group.1), c(1, rep(length(states.strategy), length(agg.strategy.diff.pc1$Group.1)))))

```

```{r diffs_alpha_ouwie_strategy_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Strategyendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("strategy.diff.alpha.pc2.", gsub(" ", ".", agg.strategy.diff.pc2$Group.1)), get)), format = "latex", caption = "Differences in Alpha values for PC2 analysis of Strategy. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.strategy, length(agg.strategy.diff.pc2$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.strategy.diff.pc1$Group.1), c(1, rep(length(states.strategy), length(agg.strategy.diff.pc1$Group.1)))))

```

```{r diffs_sigma_ouwie_strategy_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Strategyendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("strategy.diff.sigma.pc2.", gsub(" ", ".", agg.strategy.diff.pc2$Group.1)), get)), format = "latex", caption = "Differences in Sigma values for PC2 analysis of Strategy. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.strategy, length(agg.strategy.diff.pc2$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.strategy.diff.pc1$Group.1), c(1, rep(length(states.strategy), length(agg.strategy.diff.pc1$Group.1)))))

```


```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

# PC3 - Parameters

```{r results = 'asis', echo = FALSE}

if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}

```


```{r pars_ouwie_strategy_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Strategyendage."}

theta.strategy.plot.pc3 <- subset(theta.plot.pc3, disc.trait == "strategy")
theta.strategy.plot.pc3$variable <- as.character(theta.strategy.plot.pc3$variable)
theta.strategy.plot.pc3 <- theta.strategy.plot.pc3[theta.strategy.plot.pc3$value >= -10 & theta.strategy.plot.pc3$value <= 10, ]

alpha.strategy.plot.pc3 <- subset(alpha.plot.pc3, disc.trait == "strategy")
alpha.strategy.plot.pc3$variable <- as.character(alpha.strategy.plot.pc3$variable)
alpha.strategy.plot.pc3 <- alpha.strategy.plot.pc3[alpha.strategy.plot.pc3$value >= -10 & alpha.strategy.plot.pc3$value <= 10, ]

sigma.strategy.plot.pc3 <- subset(sigma.plot.pc3, disc.trait == "strategy")
sigma.strategy.plot.pc3$variable <- as.character(sigma.strategy.plot.pc3$variable)
sigma.strategy.plot.pc3 <- sigma.strategy.plot.pc3[sigma.strategy.plot.pc3$value >= -10 & sigma.strategy.plot.pc3$value <= 10, ]

theta.strategy.pc3 <-
    ggplot(na.omit(theta.strategy.plot.pc3)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.strategy) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

alpha.strategy.pc3 <-
    ggplot(na.omit(alpha.strategy.plot.pc3)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.strategy) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

sigma.strategy.pc3 <-
    ggplot(na.omit(sigma.strategy.plot.pc3)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.strategy) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Sigma") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          #strip.background.y = element_blank(),
          #strip.text.y = element_blank(),
          axis.title.x = element_blank())

(theta.strategy.pc3 + alpha.strategy.pc3 + sigma.strategy.pc3) +
    plot_annotation(tag_levels = 'A')

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

## PC3 - Parameter differences

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r diffs_theta_ouwie_strategy_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Strategyendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("strategy.diff.theta.pc3.", gsub(" ", ".", agg.strategy.diff.pc3$Group.1)), get)), format = "latex", caption = "Differences in Theta values for PC3 analysis of Strategy. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.strategy, length(agg.strategy.diff.pc3$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.strategy.diff.pc1$Group.1), c(1, rep(length(states.strategy), length(agg.strategy.diff.pc1$Group.1)))))

```

```{r diffs_alpha_ouwie_strategy_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Strategyendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("strategy.diff.alpha.pc3.", gsub(" ", ".", agg.strategy.diff.pc3$Group.1)), get)), format = "latex", caption = "Differences in Alpha values for PC3 analysis of Strategy. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.strategy, length(agg.strategy.diff.pc3$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.strategy.diff.pc1$Group.1), c(1, rep(length(states.strategy), length(agg.strategy.diff.pc1$Group.1)))))

```

```{r diffs_sigma_ouwie_strategy_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Strategyendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("strategy.diff.sigma.pc3.", gsub(" ", ".", agg.strategy.diff.pc3$Group.1)), get)), format = "latex", caption = "Differences in Sigma values for PC3 analysis of Strategy. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.strategy, length(agg.strategy.diff.pc3$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.strategy.diff.pc1$Group.1), c(1, rep(length(states.strategy), length(agg.strategy.diff.pc1$Group.1)))))

```


```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```







# Warts

# PC1 - Parameters

```{r results = 'asis', echo = FALSE}

if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}

```


```{r pars_ouwie_warts_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Wartsendage."}

theta.warts.plot.pc1 <- subset(theta.plot.pc1, disc.trait == "warts")
theta.warts.plot.pc1$variable <- as.character(theta.warts.plot.pc1$variable)
theta.warts.plot.pc1 <- theta.warts.plot.pc1[theta.warts.plot.pc1$value >= -10 & theta.warts.plot.pc1$value <= 10, ]

alpha.warts.plot.pc1 <- subset(alpha.plot.pc1, disc.trait == "warts")
alpha.warts.plot.pc1$variable <- as.character(alpha.warts.plot.pc1$variable)
alpha.warts.plot.pc1 <- alpha.warts.plot.pc1[alpha.warts.plot.pc1$value >= -10 & alpha.warts.plot.pc1$value <= 10, ]

sigma.warts.plot.pc1 <- subset(sigma.plot.pc1, disc.trait == "warts")
sigma.warts.plot.pc1$variable <- as.character(sigma.warts.plot.pc1$variable)
sigma.warts.plot.pc1 <- sigma.warts.plot.pc1[sigma.warts.plot.pc1$value >= -10 & sigma.warts.plot.pc1$value <= 10, ]

theta.warts.pc1 <-
    ggplot(na.omit(theta.warts.plot.pc1)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.warts) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

alpha.warts.pc1 <-
    ggplot(na.omit(alpha.warts.plot.pc1)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.warts) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

sigma.warts.pc1 <-
    ggplot(na.omit(sigma.warts.plot.pc1)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.warts) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Sigma") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          #strip.background.y = element_blank(),
          #strip.text.y = element_blank(),
          axis.title.x = element_blank())

(theta.warts.pc1 + alpha.warts.pc1 + sigma.warts.pc1) +
    plot_annotation(tag_levels = 'A')

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

## PC1 - Parameter differences

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r diffs_theta_ouwie_warts_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Wartsendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("warts.diff.theta.pc1.", gsub(" ", ".", agg.warts.diff.pc1$Group.1)), get)), format = "latex", caption = "Differences in Theta values for PC1 analysis of Warts. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.warts, length(agg.warts.diff.pc1$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.warts.diff.pc1$Group.1), c(1, rep(length(states.warts), length(agg.warts.diff.pc1$Group.1)))))

```

```{r diffs_alpha_ouwie_warts_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Wartsendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("warts.diff.alpha.pc1.", gsub(" ", ".", agg.warts.diff.pc1$Group.1)), get)), format = "latex", caption = "Differences in Alpha values for PC1 analysis of Warts. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.warts, length(agg.warts.diff.pc1$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.warts.diff.pc1$Group.1), c(1, rep(length(states.warts), length(agg.warts.diff.pc1$Group.1)))))

```

```{r diffs_sigma_ouwie_warts_pc1, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Wartsendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("warts.diff.sigma.pc1.", gsub(" ", ".", agg.warts.diff.pc1$Group.1)), get)), format = "latex", caption = "Differences in Sigma values for PC1 analysis of Warts. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.warts, length(agg.warts.diff.pc1$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.warts.diff.pc1$Group.1), c(1, rep(length(states.warts), length(agg.warts.diff.pc1$Group.1)))))

```


```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

# PC2 - Parameters

```{r results = 'asis', echo = FALSE}

if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}

```

```{r pars_ouwie_warts_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Wartsendage."}

theta.warts.plot.pc2 <- subset(theta.plot.pc2, disc.trait == "warts")
theta.warts.plot.pc2$variable <- as.character(theta.warts.plot.pc2$variable)
theta.warts.plot.pc2 <- theta.warts.plot.pc2[theta.warts.plot.pc2$value >= -10 & theta.warts.plot.pc2$value <= 10, ]

alpha.warts.plot.pc2 <- subset(alpha.plot.pc2, disc.trait == "warts")
alpha.warts.plot.pc2$variable <- as.character(alpha.warts.plot.pc2$variable)
alpha.warts.plot.pc2 <- alpha.warts.plot.pc2[alpha.warts.plot.pc2$value >= -10 & alpha.warts.plot.pc2$value <= 10, ]

sigma.warts.plot.pc2 <- subset(sigma.plot.pc2, disc.trait == "warts")
sigma.warts.plot.pc2$variable <- as.character(sigma.warts.plot.pc2$variable)
sigma.warts.plot.pc2 <- sigma.warts.plot.pc2[sigma.warts.plot.pc2$value >= -10 & sigma.warts.plot.pc2$value <= 10, ]

theta.warts.pc2 <-
    ggplot(na.omit(theta.warts.plot.pc2)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.warts) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

alpha.warts.pc2 <-
    ggplot(na.omit(alpha.warts.plot.pc2)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.warts) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

sigma.warts.pc2 <-
    ggplot(na.omit(sigma.warts.plot.pc2)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.warts) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Sigma") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          #strip.background.y = element_blank(),
          #strip.text.y = element_blank(),
          axis.title.x = element_blank())

(theta.warts.pc2 + alpha.warts.pc2 + sigma.warts.pc2) +
    plot_annotation(tag_levels = 'A')

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

## PC2 - Parameter differences

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r diffs_theta_ouwie_warts_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Wartsendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("warts.diff.theta.pc2.", gsub(" ", ".", agg.warts.diff.pc2$Group.1)), get)), format = "latex", caption = "Differences in Theta values for PC2 analysis of Warts. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.warts, length(agg.warts.diff.pc2$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.warts.diff.pc1$Group.1), c(1, rep(length(states.warts), length(agg.warts.diff.pc1$Group.1)))))

```

```{r diffs_alpha_ouwie_warts_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Wartsendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("warts.diff.alpha.pc2.", gsub(" ", ".", agg.warts.diff.pc2$Group.1)), get)), format = "latex", caption = "Differences in Alpha values for PC2 analysis of Warts. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.warts, length(agg.warts.diff.pc2$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.warts.diff.pc1$Group.1), c(1, rep(length(states.warts), length(agg.warts.diff.pc1$Group.1)))))

```

```{r diffs_sigma_ouwie_warts_pc2, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Wartsendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("warts.diff.sigma.pc2.", gsub(" ", ".", agg.warts.diff.pc2$Group.1)), get)), format = "latex", caption = "Differences in Sigma values for PC2 analysis of Warts. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.warts, length(agg.warts.diff.pc2$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.warts.diff.pc1$Group.1), c(1, rep(length(states.warts), length(agg.warts.diff.pc1$Group.1)))))

```


```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

# PC3 - Parameters

```{r results = 'asis', echo = FALSE}

if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}

```

```{r pars_ouwie_warts_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Wartsendage."}

theta.warts.plot.pc3 <- subset(theta.plot.pc3, disc.trait == "warts")
theta.warts.plot.pc3$variable <- as.character(theta.warts.plot.pc3$variable)
theta.warts.plot.pc3 <- theta.warts.plot.pc3[theta.warts.plot.pc3$value >= -10 & theta.warts.plot.pc3$value <= 10, ]

alpha.warts.plot.pc3 <- subset(alpha.plot.pc3, disc.trait == "warts")
alpha.warts.plot.pc3$variable <- as.character(alpha.warts.plot.pc3$variable)
alpha.warts.plot.pc3 <- alpha.warts.plot.pc3[alpha.warts.plot.pc3$value >= -10 & alpha.warts.plot.pc3$value <= 10, ]

sigma.warts.plot.pc3 <- subset(sigma.plot.pc3, disc.trait == "warts")
sigma.warts.plot.pc3$variable <- as.character(sigma.warts.plot.pc3$variable)
sigma.warts.plot.pc3 <- sigma.warts.plot.pc3[sigma.warts.plot.pc3$value >= -10 & sigma.warts.plot.pc3$value <= 10, ]

theta.warts.pc3 <-
    ggplot(na.omit(theta.warts.plot.pc3)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.warts) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

alpha.warts.pc3 <-
    ggplot(na.omit(alpha.warts.plot.pc3)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.warts) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Alpha") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          strip.background.y = element_blank(),
          strip.text.y = element_blank(),
          axis.title.x = element_blank())

sigma.warts.pc3 <-
    ggplot(na.omit(sigma.warts.plot.pc3)) +
    geom_jitter(aes(x = variable, y = value, colour = variable), alpha = 0.2, width = 0.1) +
    geom_boxplot(aes(x = variable, y = value, colour = variable), fill = NA, alpha = 0.1, lwd = 0.25, width = 0.5) +
    stat_summary(aes(x = variable, y = value), fun = "mean", geom = "point", size = 3, shape = 19) +
    scale_x_discrete(labels = states.warts) +
    theme_cowplot() +
    #coord_flip() +
    #ylim(-2, 6) +
    #coord_flip() +
    labs(x = "Discrete State", y = "Sigma") +
    facet_grid(trait ~ ., scales = "free_y") +
    theme(legend.position = "none",
          #strip.background.y = element_blank(),
          #strip.text.y = element_blank(),
          axis.title.x = element_blank())

(theta.warts.pc3 + alpha.warts.pc3 + sigma.warts.pc3) +
    plot_annotation(tag_levels = 'A')

```

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

## PC3 - Parameter differences

```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\begin{landscape}")
}
```

```{r diffs_theta_ouwie_warts_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Wartsendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("warts.diff.theta.pc3.", gsub(" ", ".", agg.warts.diff.pc3$Group.1)), get)), format = "latex", caption = "Differences in Theta values for PC3 analysis of Warts. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.warts, length(agg.warts.diff.pc3$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.warts.diff.pc1$Group.1), c(1, rep(length(states.warts), length(agg.warts.diff.pc1$Group.1)))))

```

```{r diffs_alpha_ouwie_warts_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Wartsendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("warts.diff.alpha.pc3.", gsub(" ", ".", agg.warts.diff.pc3$Group.1)), get)), format = "latex", caption = "Differences in Alpha values for PC3 analysis of Warts. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.warts, length(agg.warts.diff.pc3$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.warts.diff.pc1$Group.1), c(1, rep(length(states.warts), length(agg.warts.diff.pc1$Group.1)))))

```

```{r diffs_sigma_ouwie_warts_pc3, echo = FALSE, message = FALSE, warning = FALSE, fig.width = 13, fig.height = 9, fig.cap = "Distribution of differences in Theta (A), Alpha (B) and Sigma (C) values for the OU-based models for each continuous trait in association with different states of Wartsendage. The differences are calculated always in relation to the first state."}

kable(x = bind_cols(lapply(paste0("warts.diff.sigma.pc3.", gsub(" ", ".", agg.warts.diff.pc3$Group.1)), get)), format = "latex", caption = "Differences in Sigma values for PC3 analysis of Warts. Each cell contains the number of replicas for which the row state was higher than the column state.", escape = FALSE, digits = 3, col.names = rep(states.warts, length(agg.warts.diff.pc3$Group.1)), align = "c") %>%
    kable_styling(full_width = FALSE) %>%
    add_header_above(data.frame(c(" ", agg.warts.diff.pc1$Group.1), c(1, rep(length(states.warts), length(agg.warts.diff.pc1$Group.1)))))

```


```{r results = 'asis', echo = FALSE}
if (knitr::is_latex_output()) {
    cat("\\end{landscape}")
}
```

